A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-15 manuscript.Rmd
replace fig caption placeholder
add introduction to collabortation

```{r readme, echo=FALSE, fig.cap="A screenshot of how a change tracked in Git is represented by GitHub.  ", out.width='100%'}
knitr::include_graphics(readme)
```

@@

If you have considered what you want to tell the public about the project with a readme, have chosen a license and thought about how to make collaboration welcoming, you may publish your Git repository.

@@

>>>>

```{r readme, echo=FALSE, fig.cap="A screenshot of how a README.md is rendered/presented on GitHub.  ", out.width='100%'}
knitr::include_graphics(readme)
```

@@

If you have considered what you want to tell the public about the project with a readme, have chosen a license and thought about how to make collaboration welcoming, you may publish your Git repository.
See the section on [GitHub] on how to publish your project.

@@

Often, reproducibility is reduced to the merits it has for the reader.
However, we argue that reproducibility is vital for collaboration, not only in the sense that the consumer of a scientific product build upon it, but also that the creators work together.
The time that you invest into ensuring reproducibility, is directed at ensuring effective collaboration.
Therefore, reproducibility is at its core about collaboration.
